From Reversible Programs to \\ Univalent Universes and Back

### 2021-11-11 Pi/paper/finite.tex
Final final revisions

% The summary of what we'll do
Thus, the goal of this section is to reconcile two different approaches to defining the symmetric group -- as an
automorphism group, and as a group syntactically presented using \emph{generators} and \emph{relations}. The generators
of the group are similar to the primitive combinators in a (reversible) programming language -- the group structure
gives the composition and inverse operations, and the relations describe how these primitive combinators interact with
each other.

>>>>

% The summary of what we'll do
Thus, the goal of this section is to reconcile two different approaches to defining the symmetric group -- as an
automorphism group, and as a group syntactically presented using \emph{generators} and
\emph{relations}~\cite{matsumoto1964generateurs}. The generators of the group are similar to the primitive combinators
in a (reversible) programming language -- the group structure gives the composition and inverse operations, and the
relations describe how these primitive combinators interact with each other.
